On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-10 formal_glossary.tex
refinement of images and conclusion of formal_glossary

The formalization of the Exploitation and Black-hat Hacking processes is the
formalization of two foundational cybersecurity concepts which lay the basis
for the definition (and formalization) of the cybersecurity theory in the next
Section (Section~\ref{sec:theory}). However, the formal definition of those
processes shall (i) correlate the formal definition of agents (i.e. the
Definition~\ref{def:agent}) with the Causality principle (i.e. the
formalization of the Kripke structure in Definition~\ref{def:modallogic}), and,
most importantly, (ii) formally define a system as a structure of agents. For
the sake of clarity, we then postpone the formalization of the two processes to
the next Section.

>>>>

The formalization of the Exploitation and Black-hat Hacking processes is the
formalization of two foundational cybersecurity concepts which lay the basis
for the definition (and formalization) of the cybersecurity theory in the next
Section (Section~\ref{sec:theory}). The formal definition of those
processes shall:
\begin{itemize}
	\item in Section~\ref{sec:theory}, formally define a system as a structure of agents, and
	\item in Section~\ref{sec:process}, correlate the formal definition of agents (i.e. the
		Definition~\ref{def:agent}) with the Causality principle (i.e.
		the formalization of the Kripke structure in
		Definition~\ref{def:modallogic}). 
\end{itemize}
